Measurement and Probability in Fuzzy Quantum Theories

### 2017-02-23 prop_iop.tex
prop_iop.tex \section{Cryptodeterministic Measures} Updating...

A real or interval-valued probability is a way to model our belief
whether an event will happen or not. Classically, when we toss a coin
or throw a needle, if we know all the initial condition, we can determine
whether an event happens or not for sure~\cite{DiaconisHolmesMontgomery2007}.

>>>>

Although a real or interval-valued probability measure could be used
to model whether we believe an event will happen or not, the classical
world could be model in an simpler way. If the complete initial condition
for tossing a coin or throwing a needle is known, we can determine
whether an event happens or not for sure~\cite{DiaconisHolmesMontgomery2007}.
In another word, Newtonian physics could be modeled by a cryptodeterministic
measure defined as follow.

\begin{definition}[Cryptodeterministic Measure]\label{def:CryptodeterministicMeasures}Given
the set of events~$\events$, a \emph{cryptodeterministic measure}
is a function~$\pmeas:\events\rightarrow\left\{ 0,1\right\} $ such
that: 
\begin{itemize}
\item $\pmeas(\emptyset)=0$, 
\item $\pmeas(\Omega)=1$, 
\item for every event $E$, $\pmeas\left(\Omega\backslash E\right)=1-\pmeas\left(E\right)$
where $\Omega\backslash E$ is the complement event of $E$, and 
\item for every collection $\left\{ E_{i}\right\} _{i=1}^{N}$ of pairwise
disjoint events, $\pmeas\left(\bigcup_{i=1}^{N}E_{i}\right)=\sum_{i=1}^{N}\pmeas(E_{i})$. 
\end{itemize}
\end{definition}
